---
title: "Introduction to functions"
author: "Adolfo Alvarez"
date: '`r Sys.Date()`'
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Definition:

> A function $f$ assigns to each element $x$ in some set $S$ a unique element in a set $T$

- The set $S$ is called the **domain** of $f$ or $Dom(f)$
- For $x$ in $Dom(f)$, $f(x)$ is called the image of $x$ under $f$
- The set of all images $f(x)$ is a subset of $T$ called the image of $f$, or $Im(f)$
$$Im(f) = {f(x): x \in Dom(f)}$$

## Some examples 

- $f_1(x) = x^2$
- $f_2(x) = \sqrt(x)$
- $f_3(x) = log(x)$
- $f_4(x) = sin(x)$

Are you familiar with them?

- x is a variable, or input
- $f(x)$ is the output, which has to be uniquely determined!
- You need to know what values of x are allowed

## Graphs

The graphical representation of the previous functions are:

## Square function

$f(x) = x^2$

```{r, echo=FALSE, warning=FALSE}
x <- seq(-3,3,0.01)
plot(x,x^2, type = "l")
```

## Square root function 

$f_2(x) = \sqrt(x)$

```{r, echo=FALSE, warning = FALSE}
plot(x,sqrt(x), type = "l")
```

## Logarithmic function 

$f_3(x) = log(x)$

```{r, echo=FALSE, warning = FALSE}
plot(x,log(x), type = "l")
```

## Exponential function 

$f_4(x) = exp(x)$

```{r, echo=FALSE, warning = FALSE}
plot(x,exp(x), type = "l")
```

## Sine function

$f_5(x) = sin(x)$

```{r, echo=FALSE, warning = FALSE}
plot(x,sin(x), type = "l")
```
